Learning Auditory Similarities Between Instrumental Playing Techniques

### 2019-10-14 paper/paper.tex
introduce pipeline

@@

\ml{introduce the system globally, while stressing the ability of the system to be conditioned for one or many people (VL). consensus ou un compositeur particulier.}

>>>>

Following the above discussed matters, we propose a ranking system that is based on a processing pipeline made of two main components, see Figure \ref{fig:pipeline}. The first component projects the audio signal of the query and the items of the database in a high dimensional timbre space using the scattering transform. The second component modify the timbre space by taking into account perceptual judgments represented as a consensus clustering of the items in the dataset, as presented in Section \ref{sec:judgments}. It considers the large margin nearest neigbors to learn the weights of the reprojection.

@@
